### 2014-03-03 seminar/seminar_report/chapter3.tex
changes

%% bare_jrnl_compsoc.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE Computer
%% Society journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% andbgf
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE!
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
% The Computer Society usually requires 10pt for submissions.
%
\documentclass[10pt,journal,cspaper,compsoc]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[12pt,journal,compsoc]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  % \usepackage[nocompress]{cite}
\else
  % normal IEEE
  % \usepackage{cite}
\fi
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.
%
% Note that some packages require special options to format as the Computer
% Society requires. In particular, Computer Society  papers do not use
% compressed citation ranges as is done in typical IEEE papers
% (e.g., [1]-[4]). Instead, they list every citation separately in order
% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
% package with the nocompress option which is supported by cite.sty v4.0
% and later. Note also the use of a CLASSOPTION conditional provided by
% IEEEtran.cls V1.7 and later.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

\usepackage{amsfonts,url}
\usepackage{amssymb,amsmath}
 \usepackage{comment}

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%\usepackage[tight,normalsize,sf,SF]{subfigure}
%\else
%\usepackage[tight,footnotesize]{subfigure}
%\fi
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. Computer Society papers
% use a larger font and \sffamily font for their captions, hence the
% additional options needed under compsoc mode. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false]{caption}
%  \usepackage[font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false]{caption}
%  \usepackage[font=footnotesize]{subfig}
%\fi
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley and Jeff Goldberg.
% This package may be useful when used in conjunction with IEEEtran.cls'
% captionsoff option. Some IEEE journals/societies require that submissions
% have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.3.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% For subfigure.sty:
% \let\MYorigsubfigure\subfigure
% \renewcommand{\subfigure}[2][\relax]{\MYorigsubfigure[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat/subfig command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Efficient Community Formation \\ for Web Services}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

\author{Ehsan~Khosrowshahi~Asl,~\IEEEmembership{Member,~IEEE,}
        Jamal~Bentahar,~\IEEEmembership{Member,~IEEE,}
        Hadi~Otrok,~\IEEEmembership{Member,~IEEE,}
        and~Rabeb~Mizouni,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell is with
the Department of Electrical and Computer Engineering, Georgia
Institute of Technology, Atlanta,
GA, 30332.\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: see http://www.michaelshell.org/contact.html
\IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
\thanks{}}

% note the % following the last \IEEEmembership and also \thanks -
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
%
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~6, No.~1, January~2007}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
%
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% The publisher's ID mark at the bottom of the page is less important with
% Computer Society journal papers as those publications place the marks
% outside of the main text columns and, therefore, unlike regular IEEE
% journals, the available text space is not reduced by their presence.
% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2007 IEEE}
% or like this to get the Computer Society new two part style.
%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2007 IEEE}%
%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark (Computer Society jorunal
% papers don't need this extra clearance.)

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
Web services are loosely-coupled business applications willing to
cooperate in distributed settings within different groups called
communities. Communities aim to provide web services with better
visibility, efficiency, market share and total payoff. A number of
mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities.
However, forming optimal and stable communities as coalitions to
maximize individual and group efficiency and income is yet to be
addressed. In this paper, we propose an efficient community
formation mechanism using cooperative game-theoretic techniques,
particularly Shapley value, core, $\epsilon$-core and convex
games. We propose a mechanism for community membership requests
and selections of web services under two scenarios: (1) there is
only one community and many web services aim to join it; and (2)
web services can join different established communities. The
ultimate objective is to develop a mechanism for web services to
form stable groups allowing them to maximize their efficiency and
generate near-optimal (welfare-maximizing) communities where a
taxation-based solution is being proposed. The theoretical and
extensive experimental results show that our algorithms provide
web services and community owners, in real-world-like
environments, with applicable and near-optimal decision making
mechanisms.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

% Note that keywords are not normally used for peer review papers.
\begin{keywords}
Web services; Cooperative game theory; Community of services;
\end{keywords}}

% make the title area
\maketitle

% To allow for easy dual compilation without having to reenter the
% abstract/keywords data, the \IEEEcompsoctitleabstractindextext text will
% not be used in maketitle, but will appear (i.e., to be "transported")
% here as \IEEEdisplaynotcompsoctitleabstractindextext when compsoc mode
% is not selected <OR> if conference mode is selected - because compsoc
% conference papers position the abstract like regular (non-compsoc)
% papers do!
\IEEEdisplaynotcompsoctitleabstractindextext
% \IEEEdisplaynotcompsoctitleabstractindextext has no effect when using
% compsoc under a non-conference mode.

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}\label{s:introduction}

\IEEEPARstart{O}{ver} the past years, online services have become
part of many scalable business applications. The increasing
reliance on web-based applications has significantly influenced
the way web services are engineered. Web services provide a set of
stateless software functions accessible at a network address over
the web. The recent developments are shifting web services from
passive and individual components to autonomous and group-based
components where interaction, composition, and cooperation are the
key challenges \cite{ICWS2011-1,SCC2011-1,Baldoni2010,Younas2013}.
The main objective is to achieve a seamless integration of
business processes, applications and web services. Delivering high
quality services considering the dynamic and unpredictable nature
of the Internet is still a very critical and challenging issue.

The need for highly available and responsive services has called
for grouping and collaborative mechanisms of loosely-coupled web
services, particularly in business settings
\cite{YuB13,Younas2012,LiuBWZ13}. The idea of grouping web
services within communities and the way those communities are
engineered so that web services can better collaborate have been
proposed and investigated in
\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
Communities are virtual groups of web services having similar or
complementary functionalities \cite{Zeng:2003:QDW:775152.775211,
Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7},
but probably different non-functional quality attributes, which
form the QoS parameters. Web service communities facilitate the
discovery of web services and also provide services with better
quality. When communities are used, users send their requests to
the coordinators of those communities, which play the role of
their representatives or access points. A community coordinator is
a particular service that takes in charge the verification of
credentials of new web services before accepting them to join the
community, inviting good web services to join the community,
firing bad web services if they do not perform as expected, etc.
The coordinator of a community is responsible for all the
operations related to the management of that community
infrastructure in terms of regulating the membership and insuring
that the overall performance is satisfactory. Unlike web services
that are members of the community, the coordinator does not offer
services directly to the users, it only forwards the requests to
the suitable members. The coordinator is created by the community
owner when the community is launched. Communities aim to provide
higher service availability and performance than what individual
web services can do. The high availability of services and the
community resilience to failure are guaranteed since web services
can cooperate and replace each other within the same community and
since there is no single point of failure in the communities
architecture.

\textbf{Motivations.} Communities of web services are then
collections of functionally similar autonomous web services
sharing a coordinator or service broker as manager which also
serves as the access point to the community. In this paper, we
advocate the idea of community as a way to group web services in
order to increase the total gain of all the members where each web
service gain is more than or equal to what this web service would
obtain being outside the community. This is because the community
can provide wider visibility, better market share, higher
reputation, and better way of sharing resources. Community is an
infrastructure and being part of it should benefit the web
service, but also the community as a whole.

As argued in \cite{CSTintercommunity}, members of a web services
community can either compete or cooperate. In this paper, we
stress the intra-community cooperation (i.e., among members of the
same community) for a better inter-community competition. The main
idea is that to form a stable community in terms of membership and
to have fair distribution of the total gain among the individual
members based on their contributions, cooperative game theory,
particularly the part of coalition games, provides a very suitable
framework. For instance, we cannot leverage the theory of repeated
games as a way to model the problem, because such a theory is
suitable for situations where web services are competing with each
other so they can learn the best response by playing the game
repeatedly. In fact, it has been proved that cooperation among
competitors is an effective business model
\cite{Chetty2003,Bucklin1993}. Several concrete examples in the
businesses world are following this model such as coalitions among
competitive airlines and coalitions in the automobile sector. For
the first example, three large and well known coalitions, called
alliances, are very active, namely Star
Alliance\footnote{\url{www.staralliance.com}} (includes 28 airline
members), SkyTeam\footnote{\url{www.skyteam.com}} (has 19
members), and Oneworld\footnote{\url{ www.oneworld.com}} (groups
13 members). Airlines of the same community are competing because
each one tries to maximize its utility by gaining more market
share. However, by sharing resources and market share and having
the option of service multi-hop air tickets combined from
different airlines, each airline member of a coalition can
increase its gain by collaborating. For the second example, the
coalition among PSA Peugeot Citro\"{e}n and Toyota that creates
Toyota Peugeot Citro\"{e}n Automobile
(TPCA)\footnote{\url{www.tpca.cz/en/}} has been very successful.
This coalition allowed the three competitors to share components
for a new city car while saving money on shared costs. Our model
of cooperation between competitor web services as coalitions
within communities follows these business models. The key question
we address is when such collaborations would be beneficial for all
the agents involved? For example the three airline alliances would
not gain anything by collaborating and sharing resources with
airlines of low reputation and quality. They will lose their
market and would rather stay away from this collaboration.
Therefore, no stable community can be formed between well
established and poor airlines.

Web services in the same community are independent and autonomous.
They are self-interest and utility maximizer agents, and behave
autonomously towards maximizing their own profits using our game
theory approach. They have the freedom to leave the community
anytime if they are not satisfied about the profit they are
making. Having a community manager, only means that the management
of the community infrastructure in terms of accepting new web
services and verifying the credentials of the members is
centralized. In other words, the coordinator does not manage web
services, but does manage the community. The manager does not
dictate what the web services should do and how they should
behave. In fact, because the community is an infrastructure that
hosts different web services, membership cannot be leaved open so
that any web service can join even those having poor quality and
bad reputation. A community is a system that should accept only
particular web services, and there should be a mechanism to
control the credentials of the members. In the real case of
airlines, the three aforementioned alliances are managed by
centralized entities:
%
\begin{itemize}
%
\item Star Alliance is managed by a centralized company \emph{Star
Alliance Services
GmbH}\footnote{\url{www.staralliance.com/en/about/organisation/}};
%
\item SkyTeam has centralized core management team, \emph{SkyTeam
Central}\footnote{\url{http://www.skyteam.com/en/About-us/Organization/Management/}};
and
%
\item Oneworld is managed by its central alliance office, the
\emph{Oneworld Management Company}
(\emph{oMC})\footnote{\url{www.oneworld.com/news-information/oneworld-fact-sheets}}.
%
\end{itemize}
%
In all these alliances, accepting a new member or pending a member
is decided centrally. Regarding the second example, TPCA coalition
is also managed by a central management company based Czech
republic\footnote{\url{www.tpca.cz/en/about-us/management-tpca-en-us/}}.

\textbf{Contributions.} In this paper, we use game theory to
propose a cooperative game model for the aggregation of web
services within communities. The solution concepts of our
cooperative game seeks to find efficient ways of forming
coalitions (teams) of web services so that they can maximize their
gain and payoff, and distribute the gain in a fair way among all
the web services. Achieving fairness when the gain is distributed
among the community members is the main factor to keep the
coalition stable as no web service will expect to gain better by
deviating from the community. In other words, the coalition is
made efficient if all the members are satisfied. We analyze the
game model using two scenarios. The first one simply considers one
community and many web services interested to join it. The second
scenario, which generalizes the first one, includes the
possibility of joining different already established communities.
We first propose a representation function for communities of web
services based on their QoS attributes. By using this function, we
can evaluate the $worth$ of each community of web services. When
facing new membership requests, a typical community coordinator
checks whether the new coalition having the old and new set of web
services will keep the community stable or not. The community
coordinate will reject the membership requests if it finds out
that the new coalition would be unstable, preventing $any$ subset
of web services from gaining significantly more by deviating from
the community and joining other communities or forming new ones.
The computation of solutions for cooperative game theory problems
is combinatorial in nature and proven to be NP-complete
\cite{Algorithmic}, making this computation impractical in real
world applications. However, using the concepts of coalition
stability, we propose approximation algorithms running in
polynomial time providing web services and community coordinators
with applicable and near-optimal decision making mechanisms.

\textbf{Organization.} The rest of the paper is organized as
follows. Section \ref{s:related-work} discusses relevant related
work. Section \ref{s:preliminaries} describes the architecture,
considered parameters and some basic cooperative game theory
concepts. Section \ref{s:model} provides the problem statement and
some numerical examples for illustration. Section
\ref{s:game_solution} presents our solution model in two different
scenarios. Section \ref{s:resutls} describes our experiments and
results. Finally, Section \ref{s:conclusion} concludes the paper
and identifies future work.

\section{Related Work}\label{s:related-work}

In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
defined communities as \emph{Service Containers} which aggregate
substitutable web services providing a common functionality (same
set of operations). They abstracted \emph{Service Containers} as
web services which are created, advertised, discovered and invoked
just as elementary web services. The \emph{Container} is
considered as a manager which is responsible for web service
selection upon receiving a request on run-time. The authors have
proposed a scoring service based on non-functional requirements of
the request and web service capabilities to dynamically chose the
web service to perform the requested task. A similar concept was
proposed by Maamar et al. in
\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
web service communities as a collection of web services with a
common functionality but different QoS properties. A community
manager, upon receiving a request, delegates the request to one of
its current members. The choice is based on the performance
history and quality metrics of each web service. The authors have
proposed an efficient global web service selection algorithm in
order to approach quality constraints and preferences for
composite services which require aggregation of different types of
services to satisfy the user.

Benslimane et al. \cite{Liris-2770} have proposed a multi-layer
approach grouping similar Web services into communities and having
an interface implemented as an abstract web service for accessing
the community on top of the community layer. The interactions
between composite, management and community layers and the
bindings are performed by a generic driver called Open Software
Connectivity (OSC).

In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
service communities with centralized access across distributed web
services. They have proposed a framework for web service
management, query resolution among communities and a query caching
mechanism executed by the manager to improve the performance of
query resolution process among many distributed communities. The
key idea is to cache previous computed results for answering
future queries.

Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
proposed an architecture utilizing \emph{Contract-Net} protocol
for engineering task distribution within communities of web
services. The protocol is centrally executed by the community
manager. This architecture has been further developed in
\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
roles have been distinguished for community members: masters and
slaves. Master web services and community managers that lead
communities and are responsible for membership management. They
can invite and convince slave web services to join the community,
and attract new slave web services to their communities by
awarding them better payoff. Moreover, they can eject some slave
members from the community to improve its overall reputation if
these members are misbehaving or cannot provide the promised QoS.

>>>>

\setcounter{chapter}{2}

\chapter{Coalition Formation for Autonomous Web Services}\label{sec:coalitionformationws}

In this chapter, we present our coalition model of agent-based web
services within communities\cite{SCC2013efficient}. We start by describing the general
architecture and considered parameters for web services.
Thereafter, problem modeling and formulation will be introduced in
terms of task distribution and community revenue. Web service
cooperative games in different settings will follow along with
some simulation results.
